Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-11-07 text/supp.tex
Tweak style of heavy ts plot
Remove a todo

\clearpage
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0}
TODO ADD TOTAL NUMBER OF POINTS ON RIGHT COLUMN
\input{../analysis/stat-table}
\clearpage

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{../analysis/ts-gpdd-heavy-eg-log10-base.pdf}
\caption{
TODO WILL INDICATE UPS AND DOWNS AND MATCH STYLE TO FIG S1
  Time series for populations with Pr($\nu < 10$) $>$ 0.5 using the base
  Gompertz population model. Panels are ordered by increasing Pr($\nu < 10$).
  Vertical axes are on a log10 scale. Colours indicate taxonomic classes. The
  labels on each panel indicate Pr($\nu < 10$) $>$ 0.5, the common name for the
  species, and the Global Population Dynamics Database ID number.
}
\label{fig:heavy-ts}
\end{center}
\end{figure}

>>>>

\clearpage
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0}
\input{../analysis/stat-table}
\clearpage

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{../analysis/ts-gpdd-heavy-eg-log10-base.pdf}
\caption{
  Time series for populations with Pr($\nu < 10$) $>$ 0.5 using the base
  Gompertz population model. Panels are ordered by increasing Pr($\nu < 10$).
  Vertical axes are on a log10 scale. Colours indicate taxonomic classes. The
  labels on each panel indicate Pr($\nu < 10$) $>$ 0.5, the common name for the
  species, and the Global Population Dynamics Database ID number.
}
\label{fig:heavy-ts}
\end{center}
\end{figure}
